exponential Bradley-Terry

### 2025-09-30 inst/exponential_BT.Rmd
Hamilton not Norris

```{r checo2023}
o <- c(6,8,3,5,2,1,2,4,2,2,20,3,2,5,1,3,4,1,4,2,6,6,10) # lando norris 2024
```

@@

```{r showlike}
like
alllike <- Reduce("*",like)
alllike 
alllike/max(alllike)
S <- log(alllike)
S <- S-max(S)
S <- pmax(S,-15)
contour(S,levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
filled.contour(S)
```

>>>>

```{r checo2023}

o <- c(5,5,2,6,6,4,2,3,8,3,4,4,6,6,3,5,2,8,7,9)  # Lewis Hamilton 2023
# o <- c(7,9,9,9,6,6,7,4,3,4,1,3,1,8,5,9,6,4,10,2,12,4) # Lewis Hamilton 2024
# o <- c(6,8,3,5,2,1,2,4,2,2,20,3,2,5,1,3,4,1,4,2,6,6,10) # lando norris 2024
```

@@

```{r showlike, cache=FALSE}
options(digits=5)
like
alllike <- Reduce("*",like)
alllike 
alllike/max(alllike)
S <- log(alllike)
S <- S-max(S)
S <- pmax(S,-15)
contour(S,levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
filled.contour(S)
```
